---
title: "Stock Report"
author: ""
date: "`r format(Sys.Date())`"
output: pdf_document
geometry: margin=1.2cm
header-includes:
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage{multicol}
  - \usepackage{float}
  - \usepackage{hyperref}
  - \usepackage{listings}

fontsize: 12pt
---

<!-- R setup libraries, using python -->
```{r setup, include=FALSE, echo=FALSE}
library(reticulate)
use_python("/usr/bin/python3")
```

<!-- Execute python scripts-->
```{r, echo=FALSE, message=FALSE, results='hide'} 

source_python("main.py")

```

<!-- LaTeX preamble-->
\graphicspath{ {./rif-logos/} }
<!-- Listings setup -->
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}
<!-- Hyperlinks -->
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,      
  urlcolor=cyan,
}

<!-- Start of Document -->

\vspace{-0.5cm}
\begin{figure}[h]
  \centering
  \includegraphics[width=8cm, height=3cm]{RIF-Logo-(MaroonTransparentBackground).png}
\end{figure}
\vspace{-0.75cm}

\section*{Market Profile}
\vspace{-0.25cm}
\begin{table}[h] 
  \label{tab:table1} 
  \begin{tabular}{p{5cm}p{12cm}}
      \hline
      \multicolumn{2}{c}{`r py$TICKER` Profile} \\
      \hline
      Price & `r py$PRICE` \\
      Beta & `r py$BETA` \\
      Market Cap & `r py$MARKET_CAP` \\
      P/E & `r py$P_E` \\
      P/B & `r py$P_B` \\ 
      EPS ttm & `r py$EPS` \\
      ROE  & `r py$ROE`\% \\
      ROI & `r py$ROI`\% \\
      \hline
  \end{tabular}
\end{table}
\vspace{-0.75cm}
\section*{Stock Chart}
\vspace{-0.5cm}
\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth, height=11cm]{"./rif-logos/price-chart.png"}
  \label{fig:price-chart}
\end{figure}

\section*{Company Summary}
`r py$SUMMARY`

\section*{Financials}

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/revenue_earnings.png"}
  \label{fig:re}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/gross-profit.png"}
  \label{fig:gp}
\end{minipage}
\end{figure}

\newpage

\begin{figure}

\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/fcf.png"}
  \label{fig:fcf}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/ebit.png"}
  \label{fig:ebit}
\end{minipage}

\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/debt_short.png"}
  \label{fig:ds}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{"./rif-logos/debt_long.png"}
  \label{fig:dl}
\end{minipage}
\end{figure}


\section*{Recent News}

`r py$STORY1_DATE` \null\hfill \href{`r py$STORY1_LINK`}{[Article Link]}
\begin{lstlisting}
`r py$STORY1_SHORT`
\end{lstlisting}

`r py$STORY2_DATE` \null\hfill \href{`r py$STORY2_LINK`}{[Article Link]}
\begin{lstlisting}
`r py$STORY2_SHORT`
\end{lstlisting}

`r py$STORY3_DATE` \null\hfill \href{`r py$STORY3_LINK`}{[Article Link]}
\begin{lstlisting}
`r py$STORY3_SHORT`
\end{lstlisting}

`r py$STORY4_DATE` \null\hfill \href{`r py$STORY4_LINK`}{[Article Link]}
\begin{lstlisting}
`r py$STORY4_SHORT`
\end{lstlisting}

`r py$STORY5_DATE` \null\hfill \href{`r py$STORY5_LINK`}{[Article Link]}
\begin{lstlisting}
`r py$STORY5_SHORT`
\end{lstlisting}


\section*{Sources}

\begin{table}[h] 
  \label{tab:sources} 
  \begin{tabular}{p{8cm}p{4cm}p{6cm}}
      \multicolumn{3}{c}{} \\
      Market Profile and News & \href{https://finviz.com/}{Finviz} &  `r py$EXACT_TIME`\\ 
      \vspace{0.5cm} &  \vspace{0.5cm} & \vspace{0.5cm}\\
      Company Summary and Chart Data & \href{https://finance.yahoo.com/}{Yahoo! Finance} & `r py$EXACT_TIME`\\ 
  \end{tabular}
\end{table}

```{python, echo=FALSE, message=FALSE, results='hide'}
import slack
#import slackclient

client = slack.WebClient(token = 'xoxb-596484384067-2508309944515-moy3XWjuLDgvSjtv3tCOwShp')
client.files_upload(channels = '#sector-materials', file='./report_R.pdf')
```

